% ===============================================================
% Back matter and declarations (Discover Artificial Intelligence requirements)
% ===============================================================
\backmatter

\bmhead{Acknowledgements}
The authors thank the supervising faculty at the School of Information and
Communication Technology, Hanoi University of Science and Technology, for their
guidance throughout this work.

\section*{Declarations}

% NOTE: Discover AI requires the following statements. Funding and
% Data/Code availability are mandatory; the others are included for
% completeness. Adjust wording only if your circumstances differ.

\noindent\textbf{Funding.} This research received no specific grant from any
funding agency in the public, commercial, or not-for-profit sectors.

\noindent\textbf{Competing interests.} The authors declare that they have no
competing interests.

\noindent\textbf{Ethics approval and consent to participate.} Not applicable.
This study does not involve human participants, their identifiable data, or
biological material. The corpus consists solely of publicly available
Vietnamese legal documents from the official electronic legal codification.

\noindent\textbf{Consent for publication.} Not applicable.

\noindent\textbf{Data availability.} The Vietnamese legal QA routing dataset,
the ambiguity and conversation benchmarks, and the derived routing labels are
available from the corresponding author on reasonable request.
% TODO: Discover AI increasingly expects a repository link (e.g. Zenodo/GitHub)
% and a licence rather than "on request". If you can deposit the data, replace
% this sentence with the DOI/URL and licence.

\noindent\textbf{Code availability.} The routing pipeline, feature extractor,
Stage~1 training scripts, Stage~2 verifier prompts, and evaluation harness are
available from the corresponding author on reasonable request.
% TODO: as above, a public repository link is strongly preferred over
% "on request" for a computational-methods paper.

\noindent\textbf{Author contributions.} N.D.T.\ designed and implemented the
system, conducted all experiments, and drafted the manuscript. P.V.H.\ and
C.T.\ supervised the research, reviewed the experimental design, and revised
the manuscript. All authors read and approved the final version.
